Analyse von Common Crawl

### 2015-07-05 presentation/presentation.tex
Fix display of toc of presentation
Fix display of plots in presentation
Add table with extracted data to presentation

\subsection{Daten}
\begin{frame}{\insertsection: \insertsubsection}
\end{frame}

@@

\subsection{TLD}
\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_tld_top10}}
\end{frame}

\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_tld}}
\end{frame}

\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_tld_comparison}}
\end{frame}

\subsection{Public Suffix}
\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_pub_suffixes_top10}}
\end{frame}

\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_pub_suffixes}}
\end{frame}

\subsection{MIME-Type}
\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_mime}}
\end{frame}

\subsection{HTTPS}
\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_https}}
\end{frame}

\subsection{Encoding}
\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_charset}}
\end{frame}

\subsection{Webserver}
\begin{frame}{\insertsection: \insertsubsection}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_server}}
\end{frame}

>>>>

\subsection{Daten}
\begin{frame}{\insertsection: \insertsubsection}
    \definecolor{light-gray}{gray}{0.6}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lcl}
            \textbf{Name}      & \textbf{Datentyp} & \textbf{Beispiel} \\ \hline\hline
            UUID               & uint128           & \textcolor{light-gray}{14a939f4-2355-11e5-b5f7-727283247c7f} \\ \hline
            Zeitstempel        & string            & \textcolor{light-gray}{2015-07-06T11:03:18T} \\ \hline
            Verwendung TLS     & bool              & https ja/nein \\ \hline
            Hostname           & string            & \textcolor{light-gray}{amazon.co.uk} \\ \hline
            TLD                & string            & \textcolor{light-gray}{uk} \\ \hline
            Public Suffix      & string            & \textcolor{light-gray}{co.uk} \\ \hline
            Pfadtiefe          & uint8             & \textit{test/cool/cool.html} $\rightarrow$ \textcolor{light-gray}{3} \\ \hline
            Pfadlänge          & uint16            & \textit{test/cool/cool.html} $\rightarrow$ \textcolor{light-gray}{19} \\ \hline
            Server             & string            & \textcolor{light-gray}{apache}, \textcolor{light-gray}{nginx}, \dots \\ \hline
            Kompression        & bool              & \textcolor{light-gray}{gzip}, \textcolor{light-gray}{deflate} in \textit{Content-Encoding} \\ \hline
            Cookies            & bool              & \textit{Set-Cookie} vorhanden \\ \hline
            MIME-Typ           & string            & \textcolor{light-gray}{text/html}, \textcolor{light-gray}{application/xml}, \dots\\ \hline
            Charset            & string            & \textcolor{light-gray}{utf}, \textcolor{light-gray}{iso-8859}, \dots \\ \hline
            Verwendung von CDN & bool              & CDN ja/nein \\ \hline
            Interne Links      & uint16            & Anzahl relative Links + gleicher Host \\ \hline
            Externe Links      & uint16            & Anzahl ausgehende Links
        \end{tabular}
    }
\end{frame}

@@

\subsection{TLD}
\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_tld_top10}}
\end{frame}

\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_tld}}
\end{frame}

\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_tld_comparison}}
\end{frame}

\subsection{Public Suffix}
\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_pub_suffixes_top10}}
\end{frame}

\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_pub_suffixes}}
\end{frame}

\subsection{Mime-Type}
\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_mime}}
\end{frame}

\subsection{TLS}
\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_https}}
\end{frame}

\subsection{Encoding}
\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_charset}}
\end{frame}

\subsection{Server}
\begin{frame}{\insertsection: \insertsubsection}
    \vspace{.1cm}
    \makebox[\textwidth][c]{\includegraphics[width=1.1\textwidth]{plots/plot_server}}
\end{frame}
